Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-11 prop.tex
prop.tex \section{Introduction} Add Citations...

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007}.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers.
Our purpose here is to exploit the consequences of replacing infinitely-specified
quantum probabilities by finite number of intervals used in interval-valued
probability measures; in particular, we show that a quantum interval-valued
probability measure may not be induced by a infinitely-precise state,
but it might be more and more likely to be identified to a particular
state when the measurement resources increase.

>>>>

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Piccinini2015}.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers~\cite{Ziegler2007,weihrauch2012computable,blum2012complexity}.
Our purpose here is to exploit the consequences of replacing infinitely-specified
quantum probabilities by finite number of intervals used in interval-valued
probability measures; in particular, we show that a quantum interval-valued
probability measure may not be induced by a infinitely-precise state,
but it might be more and more likely to be identified to a particular
state when the measurement resources increase.
